---
title: "Group Project 2"
author: "XP"
date: "12/8/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Group Project 2
CAPM and a multivariate model of stock returns

Variables:            
Sector portfolio excess returns (return minus the risk free rate)
BMATRUSER:    Building materials
INDUSUSER:    Industrials
CNSMGUSER:    Consumer goods
FINANUSER:    Financials
TECNOUSER:    Technology
MktRF:   Market return - risk free rate
SMB:    Fama-French Small minus Big  
HML:    Fama- French  High minus Low 
RF:    risk free rate

```{r}
# Import Data
library(readxl)
returns <- read_excel("returns.xlsx", 
    col_types = c("date", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric"))
colnames(returns)[12] <- "MktRF"
```

CAPM estimation
************************************************************************************************************
Q1. (10 points) Estimate CAPM regressions for each of the 5 portfolios and report the results. 
             Is the CAPM rejected?
```{r}
lm1 <- lm("BMATRUSER ~ MktRF", data=returns)
summary(lm1)

lm2 <- lm("INDUSUSER ~ MktRF", data=returns)
summary(lm2)

lm3 <- lm("CNSMGUSER ~ MktRF", data=returns)
summary(lm3)

lm4 <- lm("FINANUSER ~ MktRF", data=returns)
summary(lm4)

lm5 <- lm("TECNOUSER ~ MktRF", data=returns)
summary(lm5)
```
             
*********************************************************************************************************
Q2. (6 points) Do the residuals of the CAPM regressions appear to be distributed normally, exhibit heteroskedasticity and autocorrelation? 
 Answer this question for INDUSUSER, FINANUSER, and TECNOUSER             
```{r}
plot(lm2)
acf(resid(lm2))
```
 
```{r}
plot(lm4)
acf(resid(lm4))
```
 
```{r}
plot(lm5)
acf(resid(lm5))
```
 
*********************************************************************************************************
Q3. (6 points) Compute the HAC standard errors for the CAPM regressions of INDUSUSER, FINANUSER, and TECNOUSER.
 Are they different from the OLS standard errors?
```{r}

```
 
 