---
title: "Group Project 3"
author: "XP"
date: "12/9/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Group project 3
Predictability of stock returns

Variables:  
  retdny:         monthly  return on the value-weighted market portfolio 
  retdny12:     yearly  return on the value-weighted market portfolio 
  retdny36:     3-year  return on the value-weighted market portfolio 
  dyny :           dividend to price ratio     
  bmny:           book-to market ratio     
  tbill :             1-month treasury bill      
```{r}
# Import Data
library(readxl)
predict <- read_excel("C:/Users/patri/OneDrive/Study/My own/RA/R/r_tasks/Gianni/predict.xlsx", 
    col_types = c("date", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric"))
```
  
  
  Q1. Run the regression of retdny as predicted by the first lag of dyny.
      Is the coefficient of dyny significant?  Is the overall regression significant? 
```{r}
predict$dynyL1 <- c(NA, predict$dyny[-464])
lm1 <- lm("retdny ~ dynyL1", data=predict)
summary(lm1)
```
      
Q2.  Do the residuals of this regression appear to be distributed normally, exhibit heteroskedasticity and autocorrelation? 
```{r}
plot(resid(lm1))
```

      