---
title: "Group Project 3"
author: "XP"
date: "12/9/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Group project 3
Predictability of stock returns

Variables:  
  retdny:         monthly  return on the value-weighted market portfolio 
  retdny12:     yearly  return on the value-weighted market portfolio 
  retdny36:     3-year  return on the value-weighted market portfolio 
  dyny :           dividend to price ratio     
  bmny:           book-to market ratio     
  tbill :             1-month treasury bill      
```{r}
# Import Data
library(readxl)
predict <- read_excel("C:/Users/patri/OneDrive/Study/My own/RA/R/r_tasks/Gianni/predict.xlsx", 
    col_types = c("date", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric"))
```
  
  
  Q1. Run the regression of retdny as predicted by the first lag of dyny.
      Is the coefficient of dyny significant?  Is the overall regression significant? 
```{r}
predict$dynyL1 <- c(NA, predict$dyny[-464])
lm1 <- lm("retdny ~ dynyL1", data=predict)
summary(lm1)
```
      
Q2.  Do the residuals of this regression appear to be distributed normally, exhibit heteroskedasticity and autocorrelation? 
```{r}
plot(lm1)
acf(resid(lm1))
```


Q3. Run the regression of retdny as predicted by the first lag of bmny
      Is the coefficient of bmny significant?  Is the overall regression significant? 
```{r}
predict$bmnyL1 <- c(NA, predict$bmny[-464])
lm2 <- lm("retdny ~ bmnyL1", data=predict)
summary(lm2)
```
      


Q4. Run the regression of retdny as predicted by the first lag of dyny and bmny
      Are the coefficients of the predicting variables significant?  
      Is the overall regression significant?
```{r}
lm3 <- lm("retdny ~ dynyL1 + bmnyL1", data=predict)
summary(lm3)
```


Q5. What could account for the result in Q4? 
```{r}
cor(predict$dyny,predict$bmny)
```


Q6. Run the regression of retdny as predicted by 2 lags of dyny.  
      Are the coefficients of the predicting variables significant?  
      Is the overall regression significant?   
     What can explain the difference of results using 1 instead of 2 lags of dyny?
```{r}
predict$dynyL2 <- c(NA, NA, predict$dyny[-c(463, 464)])
lm4 <- lm("retdny ~ dynyL1 + dynyL2", data=predict)
summary(lm1)
```
```{r}
summary(lm4)
```

```{r}
acf(predict$dyny)
```


Q7. Run the regression of retdny12 as predicted by the 12th lag of dyny, check normality, heteroskedasticty and autocorrelation of residuals, and compute HAC standard errors.  
      Has predictability increased?   
      Is there eveidence of non-normality, heteroskedasticty and autocorrelation of residuals?  
      What is t-stat using the HAC standard errors? Is the coefficient of dyny12 significant?
```{r}
predict$dynyL12 <- c(rep(NA, 12), predict$dyny[1:452])
lm5 <- lm("retdny12 ~ dynyL12", data=predict)
summary(lm5)
```
```{r}
plot(lm5)
acf(resid(lm5))
```


Q8. Run the regression of retdny36 as predicted by the 36th lag of dyny, check normality, heteroskedasticty and autocorrelation of residuals, and compute HAC standard errors.  
      Has predictability increased?   
      Is there eveidence of non-normality, heteroskedasticty and autocorrelation of residuals?  
      What is t-stat using the HAC standard errors? Is the coefficient of dyny36 significant?
```{r}
predict$dynyL36 <- c(rep(NA, 36), predict$dyny[1:(464-36)])
lm6 <- lm("retdny36 ~ dynyL36", data=predict)
summary(lm6)
```
```{r}
plot(lm6)
acf(resid(lm6))
```
```{r}
library(sandwich)
vcovHAC(lm6)
```
```{r}
library(lmtest)
vcv <- vcovHAC(lm6)
coeftest(lm6, vcv)
```






      
      